**The statistical analysis of non-linear longitudinal data in biomedical research using generalized additive models**

### 2021-02-08 Manuscripts/Manuscript_AM_v2.Rmd
Manuscript 2, testing graphs

 ---
title: '**The statistical analysis of non-linear longitudinal data in biomedical research using generalized additive models**'
subtitle: _Beyond repeated measures ANOVA and Linear Mixed Models_
author:
- Ariel Mundo^[Department of Biomedical Engineering, University of Arkansas, Fayetteville]
- Timothy J. Muldoon^[Department of Biomedical Engineering, University of Arkansas,
  Fayetteville]
- John R. Tipton^[Department of Mathematical Sciences, University of Arkansas, Fayetteville]
output:
  bookdown::pdf_document2:
    keep_tex: yes
    fig_caption: yes
    extra_dependencies: ["subfig","breqn"]
  bookdown::word_document2: default
  bookdown::html_document2: default
  link-citations: yes
  css: style.css
  '': default
csl: Elsevier.csl
bibliography: refs.bib
---

@@

}
```

```{r, linear-model-correlated, fig.width=16, fig.height=12,  echo=FALSE,message=FALSE,fig.show='hold',fig.cap="Simulated linear responses from two groups with a rm-ANOVA model fitted. Top row, simulated data, lines represent mean response. Bottom row, fitted model, thick lines represent predicted mean response"}
# linear response, correlated errors (subject effect)
txt<-18
plot_example(example(fun_type = "linear", error_type = "correlated")) +
  plot_annotation(tag_levels='A',
                  title = 'Simulated with linear function and correlated errors') &
   theme(plot.title = element_text(size = 20),text=element_text(size=txt)
)
```

```{r linear-model-independent, fig.width=16, fig.height=16,echo=FALSE,fig.cap='Simulated quadratic responses from two groups with an rm-ANOVA model fitted. Top row, simulated data, lines represent mean response. Bottom row, fitted model, thick lines represent predicted mean response', message=FALSE}
# quadratic response, correlated errors (subject effect)
txt<-18
plot_example(example(fun_type = "linear", error_type = "independent")) +
  plot_annotation(
    tag_levels='A',
  title = 'Simulated with linear function and independent errors') &
   theme(plot.title = element_text(size = 20),text=element_text(size=txt)
)
  # theme(plot.title = element_text(size = 20))
```

It is clear from Figure \@ref(fig:linear-model) that the fit produced by the rm-ANOVA model is good as the predictions for the mean response are reasonably close to the "truth" of the simulated data.

@@

>>>>

---
output:
  pdf_document: default
  html_document: default
---
 ---
title: '**The statistical analysis of non-linear longitudinal data in biomedical research using generalized additive models**'
subtitle: _Beyond repeated measures ANOVA and Linear Mixed Models_
author:
- Ariel Mundo^[Department of Biomedical Engineering, University of Arkansas, Fayetteville]
- Timothy J. Muldoon^[Department of Biomedical Engineering, University of Arkansas,
  Fayetteville]
- John R. Tipton^[Department of Mathematical Sciences, University of Arkansas, Fayetteville]
output:
  bookdown::pdf_document2:
    keep_tex: yes
    fig_caption: yes
    extra_dependencies: ["subfig","breqn"]
  bookdown::word_document2: default
  bookdown::html_document2: default
  link-citations: yes
  css: style.css
  '': default
csl: Elsevier.csl
bibliography: refs.bib
---

@@

}

txt<-18
A<-plot_example(example(fun_type = "linear", error_type = "correlated")) +
  plot_annotation(tag_levels='A',
                  title = 'Simulated with linear function and correlated errors') &
   theme(plot.title = element_text(size = 20),text=element_text(size=txt)
)

B<-plot_example(example(fun_type = "linear", error_type = "independent")) +
  plot_annotation(
    tag_levels='A',
  title = 'Simulated with linear function and independent errors') &
   theme(plot.title = element_text(size = 20),text=element_text(size=txt)
)

C<-plot_example(example(fun_type = "quadratic", error_type = "correlated")) +
  plot_annotation(tag_levels='A',
  title = 'Simulated with quadratic function and independent errors')&
    theme(plot.title = element_text(size = 20),text=element_text(size=txt)
)

D<-plot_example(example(fun_type = "quadratic", error_type = "independent")) +
  plot_annotation(tag_levels='A',
  title = 'Simulated with quadratic function and correlated errors')&
  theme(plot.title = element_text(size = 20),text=element_text(size=txt)
)

```

```{r, linear-models, fig.width=16, fig.height=12,  echo=FALSE,message=FALSE,fig.show='hold',fig.cap="Simulated linear responses from two groups with a rm-ANOVA model fitted. Top row, simulated data, lines represent mean response. Bottom row, fitted model, thick lines represent predicted mean response"}
# linear response, correlated errors (subject effect)
A/B+plot_annotation(tag_levels='A')
```

It is clear from Figure \@ref(fig:linear-models) that the fit produced by the rm-ANOVA model is good as the predictions for the mean response are reasonably close to the "truth" of the simulated data.

@@

```{r, quadratic-response, fig.width=16, fig.height=12,  echo=FALSE,message=FALSE,fig.show='hold',fig.cap="Simulated quadratic responses from two groups with a rm-ANOVA model fitted. Top row, simulated data, lines represent mean response. Bottom row, fitted model, thick lines represent predicted mean response"}
# linear response, correlated errors (subject effect)
C/D+plot_annotation(tag_levels='A')
```
